BACI of `r paste(params$species)` biomass for `r paste(params$region)` VOCC

### 2019-10-21 analysis/VOCC/4-vocc-BACI-multiyear.Rmd
add option for threshold selection based on width

---
title: "BACI of `r paste(params$species)` biomass for `r paste(params$region)` VOCC"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    species: "Pacific Ocean Perch" 
    region: "West Coast Vancouver Island"
    age: "imm"
    biomass_threshold: "50"
    climate: "temperature"
    threshold: 0.25
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.keep = "all", fig.show = "asis",
  fig.width = 11, fig.height = 8.5,
  echo = FALSE, warning = FALSE, message = FALSE
)
options(scipen = 999)
options(digits = 4)
```

@@

#### Set parameters
```{r }
species <- params$species
age <- params$age
region <- params$region
biomass_threshold <- params$biomass_threshold
climate <- params$climate

paste("species =", species)
paste("age =", age)
paste("region =", region)
paste("biomass_threshold =", biomass_threshold)
paste("climate =", climate)
```

#### Set default cell sizes and scale
```{r, echo=FALSE}
input_cell_size <- 2
dist_intercept <- 0 # input_cell_size / 2
scale_fac <- 1
delta_t_step <- 2
skip_time <- NULL
```

@@

all_params <- readRDS(paste0("data/root-values-by-species-by-age.rds"))
#browser()
all_params <- all_params %>% filter(covs == "x2016-log-both-trawledFALSE") %>% mutate(model_type = ifelse(grepl("total", model), "total", "split"))

if (age == "imm") {
  all_params <- filter(all_params, age == "imm")
} else {
  all_params <- filter(all_params, age != "imm")
  if (any(all_params$model_type == "split")) {
    all_params <- filter(all_params, model_type != "total")
  }
}

@@

if (climate == "temperature") {
  temp_threshold <- params$threshold

  # if more than one model option in dataframe will pick the one with highest peak density
  if (biomass_threshold == "75") {
    .upper <- root_params[rev(order(root_params$do_maxy)), ]$upper_t_75
  }
  if (biomass_threshold == "50") {
    .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_50
  }
  if (biomass_threshold == "25") {
    .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_25
  }
  .upper <- na.omit(.upper)

@@

# Calculate climate vectors
```{r }
vocc_by_year <- lapply(start_years, function(start_time) {
  try({
    vocc <- readRDS(paste0(
      "data/vocc-", ssid_string, "-", climate_string, "-",
      min_string, "to", max_string, "-", start_time, "-", delta_t_total, ".rds"
    ))
  })

  if (!exists("vocc")) {

    if (climate=="temperature") {
      climate_predictions <- readRDS("data/predicted_temp_allyears.rds") %>% mutate(temp = est)

    } else {
      pred_temp_do <- readRDS(here::here("analysis/tmb-sensor-explore/models/predicted-DO.rds"))

      if (length(variable_names) > 1) {
        climate_predictions <- replicate(length(variable_names), pred_temp_do, simplify = FALSE)
      } else {
        climate_predictions <- pred_temp_do
      }
    }
    end_time <- start_time + 2
    vocc <- make_vector_data(climate_predictions,
      variable_names = variable_names,
      ssid = model_ssid,
      start_time = start_time,
      end_time = end_time,
      skip_time = skip_time,
      input_cell_size = input_cell_size,
      scale_fac = scale_fac,
      delta_t_total = delta_t_total,
      delta_t_step = delta_t_step,
      indices = indices,
      min_thresholds = lower_change,
      max_thresholds = upper_change,
      round_fact = 10
    )

@@

    saveRDS(vocc, file = paste0(
      "data/vocc-", ssid_string, "-", climate_string, "-",
      min_string, "to", max_string, "-", start_time, "-", delta_t_total, ".rds"
    ))
  }
  vocc
})
```

### Plot all possible vectors
```{r }
if (!exists("vocc")) {
  all_vector_plots <- lapply(vocc_by_year, function(vocc) {
    start_time <- vocc$start_time[1]

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total

      vocc_plot <- plot_vocc(vocc,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("Change from\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(-4, 3),
        white_zero = TRUE,
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total

      vocc_plot <- plot_vocc(vocc,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("Change from\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste("Change from\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        white_zero = TRUE,
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vocc,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste("Change from\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

  png(
    file = paste0(
      "figs/vocc-", climate_string, min_string, "to", max_string, "-", ssid_string, ".png"
    ),
    res = 600,
    units = "in",
    width = 8.5,
    height = 11
  )
  gridExtra::grid.arrange(
    grobs = all_vector_plots,
    ncol = 2,
    top = grid::textGrob(paste("Vectors for a DO decline of", lower_change[1], "and/or temperature increase of", upper_change[2], ""))
  )
  dev.off()
}
#print(all_vector_plots)
invisible(lapply(all_vector_plots, print))
```

@@

all_vectors$var_1_min <- lower_thresholds[1]
all_vectors$var_2_min <- lower_thresholds[2]
all_vectors$var_1_max <- upper_thresholds[1]
all_vectors$var_2_max <- upper_thresholds[2]
```

### Plot remaining climate vectors for regions where change exceeds thresholds
```{r echo=FALSE, warning=FALSE}
if (climate == "temperature") {
  all_vectors$diff <- all_vectors$units_per_decade / 10 * delta_t_total
  raster_min <- min(all_vectors$diff)
  raster_max <- max(all_vectors$diff)
}

if (climate == "do") {
  all_vectors$diff <- all_vectors$units_per_decade / 10 * delta_t_total
  raster_min <- min(all_vectors$diff)
  raster_max <- max(all_vectors$diff)
}

if (climate == "do and temperature") {
  all_vectors$temp_diff <- all_vectors$temp.units_per_decade / 10 * delta_t_total
  all_vectors$do_diff <- all_vectors$do_est.units_per_decade / 10 * delta_t_total
  raster_min_temp <- min(all_vectors$temp_diff)
  raster_max_temp <- max(all_vectors$temp_diff)
  raster_min_do <- min(all_vectors$do_diff)
  raster_max_do <- max(all_vectors$do_diff)
}

@@

      vocc_plot <- plot_vocc(vectors,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        white_zero = TRUE,
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot <- plot_vocc(vectors,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vectors,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        white_zero = TRUE,
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vectors,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

#print(trimmed_vector_plots)
invisible(lapply(trimmed_vector_plots, print))
```

@@

biomass_by_year <- list()
for (j in seq_along(start_years)) {
  start_time <- start_years[[j]]
  end_time <- start_time + 2

  biomass_by_year[[j]] <- make_trend_data(biomass_predictions,
    ssid = model_ssid,
    start_time = start_time,
    skip_time = skip_time,
    end_time = end_time,
    input_cell_size = input_cell_size,
    scale_fac = scale_fac,
    delta_t_total = delta_t_total,
    delta_t_step = delta_t_step,
    indices = indices,
    variable_names = "est_exp"
  )
}

@@

>>>>

---
title: "BACI of `r paste(params$species)` biomass for `r paste(params$region)` VOCC"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    species: "Redbanded Rockfish" 
    region: "both odd year surveys"
    age: "mature"
    biomass_threshold: "50"
    climate: "temperature"
    threshold: 0.5
editor_options: 
  chunk_output_type: inline
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.keep = "all", fig.show = "asis", dpi = 600,
  fig.width = 6, fig.height = 5,
  echo = FALSE, warning = FALSE, message = FALSE
)
options(scipen = 999)
options(digits = 4)
```

@@

#### Set parameters
```{r }
species <- params$species
age <- params$age
region <- params$region
biomass_threshold <- params$biomass_threshold
climate <- params$climate
threshold <- params$threshold

paste("species =", species)
paste("age =", age)
paste("region =", region)
paste("biomass_threshold =", biomass_threshold)
paste("climate =", climate)
paste("climate change threshold =", threshold)
```

#### Set default cell sizes and scale
```{r, echo=FALSE}
max_vector <- 80
input_cell_size <- 2
dist_intercept <- 0 # input_cell_size / 2
scale_fac <- 1
delta_t_step <- 2
skip_time <- NULL
```

@@

all_params <- readRDS(paste0("data/root-values-by-species-by-age.rds"))
#browser()
all_params <- all_params %>% filter(covs == "x2016-log-both-trawledFALSE") #%>% mutate(model_type = ifelse(grepl("total", model), "total", "split"))

if (age == "imm") {
  all_params <- filter(all_params, age == "imm")
} else {
  all_params <- filter(all_params, age != "imm")
  # if (any(all_params$model_type == "split")) {
  #   all_params <- filter(all_params, model_type != "total")
  # }
}

@@

if (climate == "temperature") {

  if (threshold) { temp_threshold <- params$threshold } else {
  temp_threshold <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_50 - root_params[rev(order(root_params$t_maxy)), ]$upper_t_75
  temp_threshold <- round(temp_threshold, 2)
  }
  # if more than one model option in dataframe will pick the one with highest peak density
  if (biomass_threshold == "75") {
    .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_75
  }
  if (biomass_threshold == "50") {
    .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_50
  }
  if (biomass_threshold == "25") {
    .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_25
  }
  .upper <- na.omit(.upper)

@@

```{r}
if (climate=="temperature") {
      climate_predictions <- readRDS("data/predicted_temp_allyears_revised") %>% mutate(temp = est)

    } else {
      pred_temp_do <- readRDS("data/predicted-DO-new.rds")

      if (length(variable_names) > 1) {
        climate_predictions <- replicate(length(variable_names), pred_temp_do, simplify = FALSE)
      } else {
        climate_predictions <- pred_temp_do
      }
    }
```

# Calculate climate vectors
```{r }
vocc_by_year <- lapply(start_years, function(start_time) {
  try({
    vocc <- readRDS(paste0(
      "data/vocc-", ssid_string, "-", climate_string, "-",
      min_string, "to", max_string, "-", start_time, "-", delta_t_total, "-update.rds"
    ))
  })

if (!exists("vocc")) {
    end_time <- start_time + 2
    vocc <- make_vector_data(climate_predictions,
      variable_names = variable_names,
      ssid = model_ssid,
      start_time = start_time,
      end_time = end_time,
      skip_time = skip_time,
      input_cell_size = input_cell_size,
      scale_fac = scale_fac,
      delta_t_total = delta_t_total,
      delta_t_step = delta_t_step,
      indices = indices,
      min_thresholds = lower_change,
      max_thresholds = upper_change,
      round_fact = 10
    )

@@

    saveRDS(vocc, file = paste0(
      "data/vocc-", ssid_string, "-", climate_string, "-",
      min_string, "to", max_string, "-", start_time, "-", delta_t_total, "-update.rds"
    ))
  }
  vocc
})
```

### Plot all possible vectors
```{r }
if (!exists("vocc")) {

  all_vector_plots_w <- lapply(vocc_by_year, function(vocc) {
    start_time <- vocc$start_time[1]

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_s",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        # raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_est_s",
        fill_label = paste(" DO change\n", start_time, 
          "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        # raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        # high_fill = "Steel Blue 4",
        # low_fill = "Red 3",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_s",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vocc,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_est_s",
        fill_label = paste(" DO change\n", start_time, "to", 
          start_time + delta_t_total, ""),
        raster_alpha = 1,
        # raster_limits = c(raster_min_do, raster_max_do),
        # white_zero = TRUE,
        # high_fill = "Steel Blue 4",
        # low_fill = "Red 3",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

  png(
    file = paste0(
      "figs/vocc-", climate_string, min_string, "to", max_string, "-", ssid_string, "-absolute.png"
    ),
    res = 600,
    units = "in",
    width = 8.5,
    height = 11
  )
  gridExtra::grid.arrange(
    grobs = all_vector_plots_w,
    ncol = 2,
    top = grid::textGrob(paste("Vectors for a DO decline of", lower_change[1], "and/or temperature increase of", upper_change[2], ""))
  )
  dev.off()
}
#print(all_vector_plots)
invisible(lapply(all_vector_plots_w, print))
```

@@

all_vectors$var_1_min <- lower_thresholds[1]
all_vectors$var_2_min <- lower_thresholds[2]
all_vectors$var_1_max <- upper_thresholds[1]
all_vectors$var_2_max <- upper_thresholds[2]

if (climate == "temperature") {
  all_vectors$diff <- all_vectors$units_per_decade / 10 * delta_t_total
  # raster_min <- min(all_vectors$diff)
  # raster_max <- max(all_vectors$diff)
  raster_min <- quantile(all_vectors$diff, 0.005)
  raster_max <- quantile(all_vectors$diff, 0.995)
}

if (climate == "do") {
  all_vectors$diff <- all_vectors$units_per_decade / 10 * delta_t_total
  # raster_min <- min(all_vectors$diff)
  # raster_max <- max(all_vectors$diff)
  # 
  raster_min <- quantile(all_vectors$diff, 0.0005)
  raster_max <- quantile(all_vectors$diff, 0.9995)

}

if (climate == "do and temperature") {
  all_vectors$temp_diff <- all_vectors$temp.units_per_decade / 10 * delta_t_total
  all_vectors$do_diff <- all_vectors$do_est.units_per_decade / 10 * delta_t_total
  raster_min_temp <- min(all_vectors$temp_diff)
  raster_max_temp <- max(all_vectors$temp_diff)
  raster_min_do <- min(all_vectors$do_diff)
  raster_max_do <- max(all_vectors$do_diff)
}
```

### Plot all possible vectors
```{r }
if (!exists("vocc")) {

  all_vector_plots <- lapply(vocc_by_year, function(vocc) {
    start_time <- vocc$start_time[1]

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "#9E0142",
        # mid_fill = NULL, #"#FFFEC9", #cream
        # high_fill = "#D53E4F",#"Steel Blue 4"
        # low_fill = "#5E4FA2",
        white_zero = TRUE,
        vec_col = "white",
        vec_alpha = 0.45,
        axis_lables = FALSE,
        transform_col =  sqrt #fourth_root_power
      ) + ggtitle(climate) #+ ggpubr::theme_transparent()# +  theme_black()
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt# no_trans
      ) + ggtitle(climate)
    }

      vocc_plot_temp <- plot_vocc(vocc,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("temperature")

      vocc_plot_do <- plot_vocc(vocc,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        white_zero = TRUE,
        high_fill = "Steel Blue 3",
        low_fill = "Red 2",
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("do")

  png(
    file = paste0(
      "figs/vocc-", climate_string, min_string, "to", max_string, "-", ssid_string, ".png"
    ),
    bg = "transparent",
    res = 600,
    units = "in",
    width = 11,
    height = 17
  )
  gridExtra::grid.arrange(
    grobs = all_vector_plots,
    ncol = 2,
    top = grid::textGrob(paste("Vectors for a DO decline of", lower_change[1], "and/or temperature increase of", upper_change[2], ""))
  )
  dev.off()
}
#print(all_vector_plots)
invisible(lapply(all_vector_plots, print))
```

### Plot remaining climate vectors for regions where change exceeds thresholds
```{r echo=FALSE, warning=FALSE}

@@

      vocc_plot <- plot_vocc(vectors,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot <- plot_vocc(vectors,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot_temp <- plot_vocc(vectors,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        na_colour = "gray",
        white_zero = TRUE,
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vectors,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

print(trimmed_vector_plots)
#invisible(lapply(trimmed_vector_plots, print))
```

@@

biomass_by_year <- list()
for (j in seq_along(start_years)) {
  start_time <- start_years[[j]]
  end_time <- start_time + 2
  indices <- c(1,2)
  biomass_by_year[[j]] <- make_trend_data(biomass_predictions,
    ssid = model_ssid,
    start_time = start_time,
    skip_time = skip_time,
    end_time = end_time,
    input_cell_size = input_cell_size,
    scale_fac = scale_fac,
    delta_t_total = delta_t_total,
    delta_t_step = delta_t_step,
    indices = indices,
    variable_names = "est_exp"
  )
}

@@

### Plot climate vectors for cells with starting with greater than 5% percentile of biomass densities
```{r echo=FALSE, warning=FALSE}
# # set lower_density_threshold of cells with cumulative densities of less than 5% of peak biomass across years
bio5perc <- sum(biomass_change$start_density)*0.05
s <- sort(biomass_change$start_density)
bio_sum <- cumsum(s)
lower_density_threshold <- s[which(bio_sum>bio5perc)[1]]

alldata <- alldata %>% filter(start_density > lower_density_threshold)

# set limits same for all years based on percent change for cells with vectors
# raster_min <- min((log(alldata$end_density+1)-log(alldata$start_density+1)))
# raster_max <- max((log(alldata$end_density+1)-log(alldata$start_density+1)))
raster_min <- quantile(((alldata$end_density)-(alldata$start_density)), 0.01)
raster_max <- max((alldata$end_density)-(alldata$start_density))#, 0.9999)

# if min and max should be global rather than for cells with vectors
# raster_min <- min((biomass_change$end_density-biomass_change$start_density)/biomass_change$start_density)
# raster_max <- max((biomass_change$end_density-biomass_change$start_density)/biomass_change$start_density)

#lower_density_threshold <- quantile(alldata$start_density, 0.25, na.rm = TRUE)

# # set lower_density_threshold of cells with cumulative densities of less than 5% of peak biomass across years
# bio5perc <- sum(biomass_change$start_density)*0.05
# s <- sort(biomass_change$start_density)
# bio_sum <- cumsum(s)
# lower_density_threshold <- s[which(bio_sum>bio5perc)[1]]

biomass_vector_plots <- lapply(trimmed_vectors, function(vectors) {
  try({
    # #offset vectors so that they represent the time step before the one for biomass change
    # vectors <- vectors %>% mutate(start_time = start_time + 2, end_time = end_time + 2)

    start_time <- vectors$start_time[1]

    # set lower_density_threshold of cells with cumulative densities of less than 5% of peak biomass within years
    annual_biomass <- filter(biomass_change, start_time == !!start_time) 
    bio5perc <- sum(annual_biomass$start_density)*0.05
    s <- sort(annual_biomass$start_density)
    bio_sum <- cumsum(s)
    lower_density_threshold <- s[which(bio_sum>bio5perc)[1]]

    #vectors <- vectors %>% filter(start_time == !!start_time)

    biomass <- left_join(biomass_change, vectors, 
      by = c("icell", "x", "y", "start_time")) %>% 
      filter(start_time == !!start_time) %>% 
     # mutate(density_diff = (log(end_density+1)-log(start_density+1)) ) %>%
      mutate(density_diff = end_density-start_density,
        distance = if_else(is.na(distance), 0, distance),
        distance = if_else(start_density < !!lower_density_threshold, 0, distance),
        target_X = as.numeric(target_X), target_Y = as.numeric(target_Y),
        target_X = if_else(start_density < !!lower_density_threshold, NA_real_, target_X),
        target_Y = if_else(start_density < !!lower_density_threshold, NA_real_, target_Y),
        n_targets = if_else(distance==0, 0, n_targets)
        )
    # start_time <- biomass$start_time[1]

    vocc_plot <- plot_vocc(biomass,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "density_diff",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        # varidis_option = 
        white_zero = FALSE,
        # mid_fill = NULL,
        # high_fill = "#5E4FA2", #"Steel Blue 4"
        # low_fill = "#D53E4F",
        # high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        # low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"   
        na_colour = "red",
        vec_col = "white",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col =  sqrt # no_trans ##fourth_root_power #
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))

    vocc_plot
  })
})

#print(biomass_vector_plots)
invisible(lapply(biomass_vector_plots, print))
```

### Plot climate vectors for cells with starting with greater than 25% percentile of biomass densities
```{r echo=FALSE, warning=FALSE}
# # set lower_density_threshold of cells with cumulative densities of less than 5% of peak biomass across years
bio5perc <- sum(biomass_change$start_density)*0.05
s <- sort(biomass_change$start_density)
bio_sum <- cumsum(s)
lower_density_threshold <- s[which(bio_sum>bio5perc)[1]]

alldata <- alldata %>% filter(start_density > lower_density_threshold)

biomass_vector_plots_raw <- lapply(vocc_by_year, function(vectors) {
  try({
    # #offset vectors so that they represent the time step before the one for biomass change
    # vectors <- vectors %>% mutate(start_time = start_time + 2, end_time = end_time + 2)

    start_time <- vectors$start_time[1]

    # set lower_density_threshold of cells with cumulative densities of less than 5% of peak biomass within years
    annual_biomass <- filter(biomass_change, start_time == !!start_time) 
    bio5perc <- sum(annual_biomass$start_density)*0.05
    s <- sort(annual_biomass$start_density)
    bio_sum <- cumsum(s)
    lower_density_threshold <- s[which(bio_sum>bio5perc)[1]]

    #vectors <- vectors %>% filter(start_time == !!start_time)

    biomass <- left_join(biomass_change, vectors, 
      by = c("icell", "x", "y", "start_time")) %>% 
      filter(start_time == !!start_time)

       vocc_plot <- plot_vocc(biomass,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "start_density",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        viridis_option = "C",
        #raster_limits = c(raster_min, raster_max),
        #white_zero = TRUE,
        #high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        #low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"
        na_colour = "red",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = fourth_root_power # no_trans #
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))

    vocc_plot
  })
})

#print(biomass_vector_plots)
invisible(lapply(biomass_vector_plots_raw, print))
```

```{r}

biomass_vector_plots_trim <- lapply(trimmed_vectors, function(vectors) {
  try({
    # #offset vectors so that they represent the time step before the one for biomass change
    # vectors <- vectors %>% mutate(start_time = start_time + 2, end_time = end_time + 2)

    start_time <- vectors$start_time[1]

    # set lower_density_threshold of cells with cumulative densities of less than 5% of peak biomass within years
    annual_biomass <- filter(biomass_change, start_time == !!start_time) 
    bio5perc <- sum(annual_biomass$start_density)*0.05
    s <- sort(annual_biomass$start_density)
    bio_sum <- cumsum(s)
    lower_density_threshold <- s[which(bio_sum>bio5perc)[1]]

    #vectors <- vectors %>% filter(start_time == !!start_time)

    biomass <- left_join(biomass_change, vectors, 
      by = c("icell", "x", "y", "start_time")) %>% 
      filter(start_time == !!start_time)
